A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-19 rmtw/a6/latex8.tex
updates to thesis proposal
1. Added section descriptions to intro

2. Added notes for methodology

3. Added notes for case company description

\subsection{Research Questions}
\begin{itemize}
\item RQ1: What drives API evolution? 
\item RQ1.1: To what extent can we reverse engineer API change decisions?
% \item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
\end{itemize}

@@

\section{Case Company Description}

\section{Methodology}
Brief intro, saying we will do a case study and what data collection methods will be used. (Also citing the paper from where we steal the case study process... höst).

\subsection{Case Study Design}

\subsection{Preparation for Data Collection}

\subsection{Data Gathering}

\subsection{Data Analysis}

\subsection{Threats to Validity}

>>>>

The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study. Section II describes the case company and how it was selected. A description of our methodology is introduced in Section III.

\subsection{Research Questions}
\begin{itemize}
\item RQ1: What drives API evolution? 
\item RQ1.1: To what extent can we reverse engineer API change decisions?
%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
\end{itemize}

@@

\section{Case Company Description}
Mention the country, size and domain. 
Focus mostly on the API since that's what's relevant to our study.

Also try to get some information on the users of the API. (it might be relevant).

The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study. [Ask Richard: Do you think we can claim that our case is typical, critical, revelatory or unique? Or is our current description adequate?]

\section{Methodology}

\subsection{Research strategy and investigation methods}
• Describe and explain the research strategy and investigation methods that will be used for the project. Motivate your choice? Use relevant references.
AKA EXPLAIN WHY WE DO

Brief intro, saying we will do a case study \cite{runeson2009guidelines} and what data collection methods will be used.

Explain why case study was chosen i.e. cuz we look at something in it's natural environment (it wouldn't work to look at example data)

Another reason that the case study approach was chosen is that there is little existing research conducted in the area, and that input from the industry is vital to the success of the research. (Especially to validate if the proposed ``pitfalls''  are correct).

Explain why we chose case study compared to for example design research.

\subsection{Case Study Design and Planning}

not sure if we will need this as a section
*Do we create a case study protocol or is it too early?

\subsection{Summary of methodology}

• Research strategy (research methodology) 
AKA EXPLAIN HOW

The goal of the study is twofold

*Define what type of goal and explain why it is ( exploratory, descriptive, explanatory, or improving.)

*It will be an embedded case study since both the code and documentation will be used as a unit of analysis. (We can discuss if interviews will be a unit of analysis or not).

\subsection{Data Collection}
• data collection procedures (e.g. interviews? survey? and sampling?) 
The main form of data collection will be performed through code and documentation analysis (third degree aka independent). In addition to this analysis, interviews will be conducted. The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.

Explain how we will sample the interviewees. (Ask Imed how this will be done).

\subsection{Data Analysis}
• method for analyzing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings

How will data be analyzed?
